An FMI-Based Initialization Plugin for INTO-CPS Maestro 2

### 2020-06-30 background.tex

As described by \cref{def:challenge}, the algebraic loops introduce specific challenges in the system. This means that algebraic loops need to be handled using fixed point iterations\cite{Gomes2018}. It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step. The number of repetitions the operations should be performed depends on the characteristics of the scenario. The operations should be performed until the system converge. 
An example of applying a fixed point iteration can be seen in \cref{def:fixedpoint}, where a system containing an algebraic loop has to be initialized using fixed point iteration.

@@

However, a fixed point iteration technique is not guaranteed to convergence if the system is unstable. This means that an upper bound of the number of repetitions needs to be established to ensure termination. In the case of a non-converging algebraic loop, the simulation should be stopped since the result of the co-simulation scenario would not be trustworthy. The criteria of a valid co-simulation scenario is specified in \cref{def:convergence}.

>>>>

As described by \cref{def:challenge} the algebraic loops introduce certain challenges in the system. This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018}. It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step. The number of repetitions the operations should be be performed depends on the characteristics of the scenario. The operations should be performed until the system converge. 
An example of applying a fixed point iteration can be seen in \cref{def:fixedpoint} where a system containing an algebraic loop has to be initialized using fixed point iteration.
\claudio{Perhaps later you can ditch \cref{fig:fixedpont} and refer to the case study section, to shorten the text.}

@@

However a fixed point iteration technique is not guaranteed to convergence if the system is unstable. This means that an upper bound of the number of repetitions needs to be established to ensure termination. In case of a non-converging algebraic loop the simulation should be stopped since the result of the co-simulation scenario would not be trustworthy. The criteria of a valid co-simulation scenario is specified in \cref{def:convergence}.

### 2020-06-30 conclusion.tex

\section{Concluding remarks}\label{sc:summary}
This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario. The calculated initialization order is optimized to group variables with similar characteristics to perform the fewest possible operations in the initialization procedure.
This approach supports the initialization of a co-simulation scenario containing algebraic loops by utilization of fixed point iteration. The approach does also discard all co-simulation scenarios which are not adhering to the law of convergence \ref{def:convergence}.
This approach can be combined with an arbitrary master algorithm to run the co-simulation. \\
The approach was realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\
Future work includes formal verification of the plugin using the Logika framework\cite{inbook}.
Future work will also look into the generation of a verification strategy for the whole Maestro 2 framework to explore how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.

\paragraph*{\textbf{Acknowlegements.}}We would like to thank Stefan Hallerstede and Peter Gorm Larsen for providing valuable input to this paper and the developed plugin.

>>>>

\section{Concluding remarks}\label{sc:summary}
This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario. The plugin optimizes the calculated initialization order by grouping variables with similar characteristics to perform the fewest possible operations in the initialization procedure.
This approach supports the initialization of a co-simulation scenario containing algebraic loops by utilization of fixed point iteration. The approach discards all co-simulation scenarios, not adhering to the law of convergence \ref{def:convergence}.
It is possible to combine the approach with an arbitrary master algorithm to run a co-simulation. \\
The approach is realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\
Future work includes formal verification of the plugin using the Logika framework\cite{inbook}.
Future work will look into the generation of a verification strategy for the whole Maestro 2 framework to examine how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.

\paragraph*{\textbf{Acknowlegements.}}We would like to thank Stefan Hallerstede, Christian Møldrup Legaard, and Peter Gorm Larsen for providing valuable input to this paper and the developed plugin.
